Bioverse: Origins of Life

### 2024-06-24 src/tex/ms.tex
plot grid points from HAZMAT paper.

\todo[inline]{biosignatures: Focus on molecular Oxygen? Excess Methane? \citep[e.g.,][]{Seeburger2023}}
% detecting methanogenic life: Sandora2020, Wang2018,
A commonly discussed biosignature is molecular Oxygen (O$_2$), which on Earth emerged as a byproduct of photosynthesis during the Proterozoic era.
No individual component of an atmosphere has been identified as a reliable biosignature in isolation~\citep{Seager2016}, and the detection of Oxygen alone will certainly not be sufficient to confirm the presence of life.
Nevertheless, we focus here on detecting this key absorber as it represents the general inherent observational challenges and trends.

@@

\begin{figure*}
    \script{hz_nuv_evo.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/hz_nuv_evo}
        \caption{Interpolated stellar luminosity evolution (left) and evolution of the \gls{NUV} flux in the \gls{HZ} as a function of host star mass. The scatter plot shows age and host star mass of the transiting planets in the synthetic sample. % with \gls{EEC} highlighted in green.
        A few example tracks are shown, where extended overlap of \gls{HZ} occupancy and high \gls{NUV} flux (green sections) fulfill our requirement for abiogenesis.
        Planet~1 is an \gls{EEC} that never receives sufficient \gls{NUV} flux for abiogenesis.
        Planet~2 and Planet~3 enter the \gls{HZ} at different times and receive sufficient \gls{NUV} flux for different durations until their respective host star evolves below the threshold.
        }
        \label{fig:hz_nuv_evo}
    \end{centering}
\end{figure*}

>>>>

% detecting methanogenic life: Sandora2020, Wang2018, Seeburger2023
A commonly discussed biosignature is molecular Oxygen (O$_2$), which on Earth emerged as a byproduct of photosynthesis during the Proterozoic era.
No individual component of an atmosphere has been identified as a reliable biosignature in isolation~\citep{Seager2016}, and the detection of Oxygen alone will certainly not be sufficient to confirm the presence of life.
Nevertheless, we focus here on detecting this key absorber as it represents the general inherent observational challenges and trends.

@@

\begin{figure*}
    \script{hz_nuv_evo.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/hz_nuv_evo}
        \caption{Interpolated stellar luminosity evolution (left) and evolution of the \gls{NUV} flux in the \gls{HZ} (right) as a function of host star mass.
        The scatter plots show age and host star mass of the transiting planets in the synthetic FGK sample; crosses denote the estimated \gls{NUV} values in \citet{Richey-Yowell2019}. % with \gls{EEC} highlighted in green.
        A few example tracks are shown, where extended overlap of \gls{HZ} occupancy and high \gls{NUV} flux (green sections) fulfill our requirement for abiogenesis.
        Planet~1 is an \gls{EEC} that never receives sufficient \gls{NUV} flux for abiogenesis.
        Planet~2 and Planet~3 enter the \gls{HZ} at different times and receive sufficient \gls{NUV} flux for different durations until their respective host star evolves below the threshold.
        }
        \label{fig:hz_nuv_evo}
    \end{centering}
\end{figure*}
